---
title: "Project 2 Group 3 Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data

```

# Survey Overview {data-orientation=columns}

Overview of survey responses
  
## row {data-width=300}





### Usable Responses

```{r,echo=FALSE}

```    
 
    



## row {data-height=600}

### Internships by State

```{r,echo=FALSE}

```


### Distribution of Number of Internships
    
```{r,echo=FALSE}



```
   
   

# Internship Effects on Salary {data-orientation=columns}

## Column {data-width=400}

### Mean Salary by Number of Internships

```{r,echo=FALSE}

```




## Column {data-width=600}

### Regression Model Predicting Salary by Number of Internships

```{r,echo=FALSE}

```

 


